\textls[-0]{\thetitle}

### 2023-03-04 lang-design.tex
Definite Article
make all comments into pdf comment from reviewer.

\cref{fig:stlc-mechanized} shows how STLC and its extension with
fixpoints can be mechanized using \Lang, in a style envisioned in
\cref{fig:stlc-nonmechanized}, directly adopted from \citet{sf-pl}. % Review B.244 - mention non-capture avoiding, SF is using non-capture avoiding.
The base family "STLC" hosts the STLC metatheories, from abstract syntax
to the type-safety theorem.
Family "STLCFix", derived from "STLC", makes adjustments as needed by a fixpoints extension:
it adds new constructors to the inductive types (\lsti{FInductive}) and
adds new cases to the recursive functions (\lsti{FRecursion}) and
induction proofs (\lsti{FInduction}).
Existing constructors and cases, as well as those definitions and
theorems that need no adjustments ("ty", "env", "empty", "steps", and
"typesafe"), are automatically inherited and reused.
In particular, executing the last command, \lsti{Check STLCFix.typesafe},
displays the type-safety theorem of the fixpoints extension.

@@

In family "STLCFix", the inductive type "tm" \emph{further binds} the "tm" type
in family "STLC". It has five constructors: four inherited from
"STLC" and a fifth called "tm_fix".

>>>>

\cref{fig:stlc-mechanized} shows how STLC and its extension with
fixpoints can be mechanized using \Lang, in a style envisioned in
\cref{fig:stlc-nonmechanized}, directly adopted from \citet{sf-pl}. \rB{mention non-capture avoiding}\EDJreply{SF is using non-capture avoiding. Is mentioning SF here enough?}
The base family "STLC" hosts the STLC metatheories, from abstract syntax
to the type-safety theorem.
Family "STLCFix", derived from "STLC", makes adjustments as needed by a fixpoints extension:
it adds new constructors to the inductive types (\lsti{FInductive}) and
adds new cases to the recursive functions (\lsti{FRecursion}) and
induction proofs (\lsti{FInduction}).
Existing constructors and cases, as well as those definitions and
theorems that need no adjustments ("ty", "env", "empty", "steps", and
"typesafe"), are automatically inherited and reused.
In particular, executing the last command, \lsti{Check STLCFix.typesafe},
displays the type-safety theorem of the fixpoints extension.

@@

In family "STLCFix", the\rD{l175}\EDJreply{Then do we add definite article in front of family "STLCFix"?} inductive type "tm" \emph{further binds} the "tm" type
in family "STLC". It has five constructors: four inherited from
"STLC" and a fifth called "tm_fix".
